---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document: 
    keep_md: yes
---

## Loading and preprocessing the data

```{r load}
library(dplyr)
library(ggplot2)

Raw_Data<-read.csv("activity.csv")
Raw_Data$date<-as.Date(Raw_Data$date)
Clean_Data<-na.omit(Raw_Data)
```

## What is mean total number of steps taken per day?

```{r mean}
Total_Steps_Data<-Clean_Data%>%
    group_by(date)%>%
    summarise(Daily_steps = sum(steps, na.rm = TRUE))

hist(Total_Steps_Data$Daily_steps,
     main = "Total number of steps taken per day",
     xlab = "Total steps taken per day",
     breaks = seq(0,25000, by=2500))

mean<-mean(Total_Steps_Data$Daily_steps)
median<-median(Total_Steps_Data$Daily_steps)

```

The mean is `r mean` and the median is `r median`.


## What is the average daily activity pattern?

```{r avg}
Interval_Steps_Data<-Clean_Data%>%
    group_by(interval)%>%
    summarise(Avg_steps = mean(steps, na.rm = TRUE))

with(Interval_Steps_Data,plot(interval,Avg_steps,
                              type="l",
                              lwd = 2,
                              xlab="Interval",
                              ylab="Average number of steps",
                              main="Average number of steps per intervals"))

interval<-max(Interval_Steps_Data$Avg_steps)
```

The 5-minute interval that, on average, contains the maximum number of steps is `r interval`.

## Imputing missing values

```{r Missing_Values}
Missing_Values_Count<-nrow(Raw_Data)-nrow(Clean_Data)

Complete_Data<-Raw_Data
for(i in 1:nrow(Complete_Data)){
    if(is.na(Complete_Data$steps[i])){
      if(i%%288==0){j=288}
      else{j=0}
        Complete_Data$steps[i]<-Interval_Steps_Data$Avg_steps[i%%288+j]
    }
}

Complete_Total_Steps_Data<-Complete_Data%>%
    group_by(date)%>%
    summarise(Daily_steps = sum(steps, na.rm = TRUE))

hist(Complete_Total_Steps_Data$Daily_steps,
     main = "Total number of steps taken per day",
     xlab = "Total steps taken per day",
     breaks = seq(0,25000, by=2500))

c_mean<-mean(Complete_Total_Steps_Data$Daily_steps)
c_median<-median(Complete_Total_Steps_Data$Daily_steps)
```

There are `r Missing_Values_Count` missing values in the dataset.
After entering the missing values, the mean is `r c_mean` and the median is `r c_median`.

## Are there differences in activity patterns between weekdays and weekends?

```{r pattern}
Complete_Data$Day<-weekdays(Complete_Data$date)

for(k in 1:nrow(Complete_Data)){
    if(Complete_Data$Day[k]=="Saturday"|Complete_Data$Day[k]=="Sunday"){
        Complete_Data$Week[k]<-"Weekend"
    }
    else{
        Complete_Data$Week[k]<-"Weekday"
    }
}

Week_Interval_Steps_Data<-Complete_Data%>%
    group_by(interval,Week)%>%
    summarise(Avg_steps = mean(steps, na.rm = TRUE))

plot<- ggplot(Week_Interval_Steps_Data,
              aes(x = interval, y = Avg_steps,color = Week)) +
    geom_line() +
    labs(title = "Average daily steps by type of date", x = "Interval", y = "Average number of steps") +
    facet_wrap(~Week, ncol = 1, nrow=2)
print(plot)
```